The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-06-23 src/ms.tex
Update src/ms.tex
Co-authored-by: Derek Homeier <dhomeie@gwdg.de>
Update src/ms.tex
Co-authored-by: Eero Vaher <eero.vaher@gmail.com>

\astropytable is \astropypkg's most general container for array-valued data.
Rather than requiring component data be converted to a
\astropyapidoc{table.Column}{table.Column}, a well-defined protocol has been
developed for any array-valued data to be used in a \astropytable, without
having to convert the data. The protocol for mixing column types, which \astropypkg
terms ``mixin''-columns, provides the same familiar table API, yet loses none
the object's data or attributes. Note ``mixin'' here does not refer to Python's
inheritance definition. Rather, it is a composition protocol that makes it
possible to store \astropy native objects -- including \astropyTime,
\astropyQuantity, and \astropySkyCoord\ -- within a \astropyTable\ and write
these to various file formats, such as FITS. For objects not already covered by
the astropy mixin-protocol, functions can be registered with \astropyTable\ to
enable interoperability. As an example, \astropypkg already implements these
mixin functions to integrate \package{dask} arrays with \astropyTable, allowing
cloud-stored or cluster-scale data to be used as a column in a \astropyTable.

>>>>

\astropytable is \astropypkg's most general container for array-valued data.
Rather than requiring component data be converted to a
\astropyapidoc{table.Column}{table.Column}, a well-defined protocol has been
developed for any array-valued data to be used in a \astropytable, without
having to convert the data. The protocol for mixing column types, which \astropypkg
terms ``mixin''-columns, provides the same familiar table API, yet loses none
the object's data or attributes. Note that ``mixin'' here is not implemented
in the commonly used Python scheme of multiple inheritance.
Rather, it is a composition protocol that makes it
possible to store \astropy native objects -- including \astropyTime,
\astropyQuantity, and \astropySkyCoord\ -- within a \astropyTable\ and write
these to various file formats, such as FITS. For objects not already covered by
the \astropypkg mixin-protocol, functions can be registered with \astropyTable\ to
enable interoperability. As an example, \astropypkg already implements these
mixin functions to integrate \package{dask} arrays with \astropyTable, allowing
cloud-stored or cluster-scale data to be used as a column in a \astropyTable.
